Experiences designing and building a PRAGMA Cloud Scheduler

### 2015-08-14 paper.tex
Few small changes

\maketitle
\begin{abstract}
PRAGMA is a community of research scientists and institutions from around the Pacific Rim that work together to enable scientific expeditions in areas of biodiversity distribution and lake ecology.  Over the past four years, the technology focus for PRAGMA's testbed has shifted to cloud and software defined networking as enabling technologies.  This short paper describes the design of a simple cloud scheduler built on top of a Web reservation system that will enable users to easily run and manage virtual clusters for their science.   It is also equally important that there be a low barrier to entry for PRAGMA institutions to become part of the PRAGMA cloud testbed and install the needed software.  Therefore, the cloud scheduler  has a simple client-server architecture and will be built upon existing technologies such as pragma\_boot, Personal Cloud Controller,  virtual network overlays (e.g.,. IPOP), and  and also a Web reservation system.  We discuss our experiences implementing our pilot cloud scheduler and then describe future work.

>>>>

\maketitle
\begin{abstract}
PRAGMA is a community of research scientists and institutions from around the Pacific Rim that work together to enable scientific expeditions in areas such as  biodiversity distribution and lake ecology.  PRAGMA's members collaborate on a testbed infrastructure and over the past four years, the technology focus has shifted to cloud and software defined networking as enabling technologies.  This short paper describes the design of a simple cloud scheduler that will 1) enable users to easily run and manage virtual clusters for their science experiments, and 2) require minimal effort for PRAGMA members to participate in.  .   It is also equally important that there be a low barrier to entry for PRAGMA institutions to become part of the PRAGMA cloud testbed and install the needed software.  Therefore, the cloud scheduler  has a simple client-server architecture and will be built upon existing technologies such as pragma\_boot, Personal Cloud Controller,  virtual network overlays (e.g.,. IPOP), and  and also a Web reservation system.  We discuss our experiences implementing our pilot cloud scheduler and then describe future work.    built on top of a Web reservation system that will
